Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-07-31 reviews/rebuttal.tex

\documentclass[10pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{calc}
\newcommand{\x}{$\times$~}

\makeatletter
\newcommand{\DESCRIPTION@original@item}{}
\let\DESCRIPTION@original@item\item
\newcommand*{\DESCRIPTION@envir}{DESCRIPTION}
\newlength{\DESCRIPTION@totalleftmargin}
\newlength{\DESCRIPTION@linewidth}
\newcommand{\DESCRIPTION@makelabel}[1]{\llap{#1}}%
\newcommand{\DESCRIPTION@item}[1][]{%
  \setlength{\@totalleftmargin}%
       {\DESCRIPTION@totalleftmargin+\widthof{\textbf{#1 }}-\leftmargin}%
  \setlength{\linewidth}
       {\DESCRIPTION@linewidth-\widthof{\textbf{#1 }}+\leftmargin}%
  \par\parshape \@ne \@totalleftmargin \linewidth
  \DESCRIPTION@original@item[\textbf{#1}]%
}
\newenvironment{DESCRIPTION}
  {\list{}{\setlength{\labelwidth}{0cm}%
           \let\makelabel\DESCRIPTION@makelabel}%
   \setlength{\DESCRIPTION@totalleftmargin}{\@totalleftmargin}%
   \setlength{\DESCRIPTION@linewidth}{\linewidth}%
   \renewcommand{\item}{\ifx\@currenvir\DESCRIPTION@envir
                           \expandafter\DESCRIPTION@item
                        \else
                           \expandafter\DESCRIPTION@original@item
                        \fi}}
  {\endlist}
\makeatother

\address{M. Andrew Jansen\\School of Life Sciences\\Arizona State University\\Tempe, AZ 85287-4501} 
\signature{\underline{Contact Information}\\email: majanse1@asu.edu\\office: 1-(480)-727-9692} 
\begin{document} 
\begin{letter}{Juan J. Morrone\\Universidad Nacional Aut\'{o}noma de M\'{e}xico\\Academic Editor, PeerJ} 
	\opening{Dear Dr. Morrone,}

	We thank you for a speedy and very constructive review of our manuscript.
	In our revised resubmission, we have made a great effort to accommodate the suggestions brought up through the review, as outlined point-by-point below (line numbers refer to diff.pdf).
	The comments of the reviewers may be found at the end of this document for your reference.
	We sincerely hope that you will find these revisions fitting and satisfactory.

	\begin{enumerate}
		\item In response to Reviewer 2, we have changed all instances of the word revision (lines 28, 200, 912, and 1077) to read either ``review'' or ``study''.
		\item In response to Reviewer 2, we did not move the first paragraph and itemized explanation of the taxonomic concept approach to the \textbf{Methods} section of the manuscript; we feel that an upfront explanation of our approach, and especially the meaning of the taxonomic concept labels, is warranted to avoid confusion while reading the introduction.
		\item In response to Reviewers 2 \& 3, we have italicized the genus name \textit{Minyomerus} in line 210.
		\item In response to Reviewer 2, we have re-written the \textbf{Natural History} subsection of the description of \textit{Minyomerus ampullaceus} (lines 333--341) to indicate that the specimen most likely came from the gut contents of a roadrunner, rather than a nest, as we had originally thought.
		\item In response to Reviewer 2, we have added a statement to the \textbf{Natural History} subsection of the description of \textit{Minyomerus tylotos} (lines 467--468) to indicate that the specific epithet of the host plant was misspelled on the label of the holotype.
		\item In response to Reviewer 3, one of the female \textit{Minyomerus franko} paratypes from the CMNC has been exchanged for a female paratype of \textit{Minyomerus sculptilis} from the USNM (lines 458, 563).
		\item In response to Reviewer 3, a single space indent was removed from the species entry for \textit{Minyomerus gravivultus} in the \textbf{Checklist of Species}, after line 689.
		\item In response to Reviewer 3, lines 709--714 were moved to the \textbf{Phylogenetic analysis} subsection of the \textbf{Methods} section (lines 170--175).
		\item In response to Reviewer 3, we have added a short explanation to the \textbf{Phylogenetic analysis} subsection of the \textbf{Methods} section outlining our general approach to multi-state character coding (lines 175--178).
		\item In response to Reviewer 3, we have clarified the description of character 6 to read ``Prementum, anterior margin medially with a distinct facet, rather than a single edge edge, that continues to lateral margins'' (lines 740--741).
		\item In response to Reviewer 3, we have clarified the description of character 28 to read ``Legs, relative length of mesotarsi to mesotibiae: (0) tarsi less than 3/4\x length of tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi shorter than tibiae, but longer than 3/4\x length of tibiae.'' (lines 821--823).
		\item In response to Reviewer 3, we have checked again that the species \textit{Minyomerus tylotos} is, in fact, flightless, and found that there are indeed no traces of wings or associated flight structures in our dissected specimens, per the species description.
		\item In keeping with the submission checklist, we have moved our funding statement from the \textbf{Acknowledgments} section (lines 1079--1081) to a separate \textbf{Funding Statement} section (lines 1099--1102), ending with the sentence: ``There was no additional external funding received for this study.''
	\end{enumerate}

	Please let us know if these revisions are acceptable.
	We thank you for your time and consideration, and look forward to next steps.

	\closing{Sincerely,\\Andrew Jansen \& Nico Franz}
	\cc{Nico M. Franz}
	%\ps{adding a postscript}
	\encl{Reviewer comments and annotations}

	\newpage
	\textsc{Reviewer Comments \& Annotations}

	\textbf{Reviewer 1 (Anal\'{i}a Lanteri)}

	\emph{Basic reporting}

	The manuscript is written in clear, unambiguous and professional English language. 
	The main objective of this work is to describe four new species of the weevil genus \textit{Minyomerus} (Curculionidae, Entiminae, Tanymecini), previously revised by the authors of the article, and to integrate the new findings in an updated key and a phylogenetic analysis based on morphological characters.

	The article is well organized and the structure conforms to PeerJ Standards. 
	The introduction includes the necessary information and background on the taxon under study. The literature is well referenced and relevant.

	The taxonomic study was based on a sufficient number of specimens collected by the authors and borrowed from different entomological collections. 
	The descriptions are very detailed and the structures of diagnostic value are illustrated with very good photographs (dorsal and lateral habitus, mouthparts, sternites VIII of female, spermathecae). 
	All figures are relevant, high quality and well labeled. The literature is well referenced and relevant.

	\emph{Experimental design}

	The new species described have been registered in ZooBank, and the information on LSID’s in provided. 
	A cladistic analysis was performed on a data matrix of 52 morphological characters and 26 terminal taxa (5 outgroups and 21 ingroups), to see the position of the new species in the context of Minyomerus and related genera. The selection of characters and character states was correct. 
	The most parsimonious tree was found using TNT, and NONA was used for the optimization of the characters. 
	The tree with the characters optimized was conveniently illustrated. 
	The cladistics methods are sufficiently detailed and the information given can be replicated.
	The potential distribution of each new species was assessed applying an ecological modeling approach, using MAXENT, and was shown in maps.

	The authors adopted the taxonomic concept approach, including the use of taxonomic concept labels and Region Connection Calculus (RCC–5) articulations and alignments.
	I am not very familiar with this approach and I find it a bit confusing for reading the results, but I understand that the authors are leaders in this matter, not yet commonly used in the taxonomic papers.
	The details of the RCC–5 alignment are given in free text form in the Supplemental Information, which also describes the content of the data input and output files.

	\newpage
	\emph{Validity of the findings}

	The work provides new taxonomic information.
	The descriptions of the new species are well justified, same as the results of the cladistics analysis.
	In the discussion, the authors compared the results of the new phylogeny with those previously obtained.
	They discussed on the intrageneric relationships and the phylogenetic position of each species in a historical-biogeographic context.
	In find it interesting and not excessively speculative, however, I have some difficulties in following the indication relative to the taxonomic concept approach.

	Conclusions are well stated, linked to original research question and limited to supporting results.

	\emph{Comments for the Author}

	The paper provides new basic taxonomic information, consisting on a description of four new weevil species, rigorously described and illustrated.
	The phylogenetic placement of these species is analyzed and their geographic ranges are discussed in relation to those of their putative sister taxa, based on the results of a niche modeling analysis.
	The methods applied are classical and correct.
	All the figures are appropriate and necessary.

	In my opinion, the taxonomic concept approach applied in this paper is somewhat confusing, as well as the supplementary information relative to this subject, but I am not an expert on this matter.

	\emph{Annotated manuscript}

	An annotated manuscript was not provided.

	\newpage	
	\textbf{Reviewer 2 (Robert Anderson)}

	\emph{Basic reporting}

	This is a comprehensive, well-written followup to the authors previous paper revising the genus \textit{Minyomerus}.
	I have made a few minor comments in the text of the manuscript PDF.
	I am quite sure that the single specimen of \textit{M. ampullaceus} is from the stomach/gut contents of a roadrunner.
	The USNM was quite active in the mid 1900's in supporting identification of gut contents from various species of birds.
	I have a new \textit{Phyxelis} from Louisiana known only from USNM specimens from quail stomach contents and the weevil \textit{Glaphyrometopus ornithodorus} was described from a series of USNM specimens from meadowlark stomach contents.
	As such, the paragraph related to the natural history of this species should be rewritten.

	The phylogenetic work appears to be well supported and discussed with all characters and states well-explained.
	As the authors know, I am not a fan of the taxonomic concept approach but I can understand the authors rationale for its use.
	The authors have done a nice job of integrating the 4 new species into the key and phylogeny and presenting these results.

	\emph{Experimental design}

	See above.

	\emph{Validity of the findings}

	See above.

	\emph{Comments for the Author}

	See above.

	\emph{Annotated manuscript}

	The reviewer has also provided an annotated manuscript as part of their review:

	\begin{DESCRIPTION}
		\item[Line 17:] ``I think review is a better term here.''
		\item[Lines 28--40:] ``I think this section is best placed in the Methods section.''
		\item[Line 200:] ``italics''
		\item[Lines 320--323:] ``I am quite sure this specimen would have been taken from the stomach contents of this species of bird.
			Over the years the USNM frequently assisted with identifications of stomach contents of various bird species.
			I know of at least two other weevil species originally known only from the stomachs of meadowlark and quail.
			Given the specimen condition this fits with this proposal.''
		\item[Lines 440, 451:] ``Is hastula or hastulata correct...see above under Holotype?''
	\end{DESCRIPTION}

	\newpage

	\textbf{Reviewer 3 (Lourdes Chamorro)}

	\emph{Basic reporting}

	No comment.

	\emph{Experimental design}

	I suggested in the pdf itself that some information may need to be added in the methods section regarding additive/non-additive coding of multistate characters.

	\emph{Validity of the findings}

	No comment.

	\emph{Comments for the Author}

	This is a thorough study that aims to describe and phylogenetically place 4 new species of \textit{Minyomerus}.
	The use of occurrence data to predict distribution ranges for each species is a much welcome approach to this type of study.

	\emph{Annotated manuscript}

	The reviewer has also provided an annotated manuscript as part of their review:

	\begin{DESCRIPTION}
		\item[Line 200:] ``Italics needed.''
		\item[Line 481:] ``?''
		\item[Line 546:] ``USNM is willing to donate this specimen to CMNC in exchange for one of the CMNC paratypes of Minyomerus franko.''
		\item[Line 672:] ``Fix slight indent.''
		\item[Lines 692--697:] ``Perhaps some or all of this would be better placed under methods.''
		\item[Table 1:] ``Why coded as additive vs non-additive?
			Nevermind, I see you expand on this below under each character.
			Perhaps something alluding to this methodology should be mentioned in the methods.''
		\item[Line 723:] ``This is rather unclear.''
		\item[Line 803:] ``This is rather vague, as well as state 2.''
		\item[Figure 23:] ``Is this species flightless also?
			It seems to have much more prominent humeri than the other species in the genus.''
		\item[Figure 35:] ``Excellent!''
	\end{DESCRIPTION}
\end{letter} 
\end{document}

### 2018-07-31 tex/revised_manuscript.tex
rebuttal and revisions

\begin{abstract}
	This contribution adopts the taxonomic concept approach, including the use of \textit{taxonomic concept labels} (name sec. [\textit{according to}] source) and Region Connection Calculus (RCC--5) articulations and alignments. 
	Prior to this study, the broad-nosed weevil genus \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) contained 17 species distributed throughout the desert and plains regions of North America.
	In this revision of \textit{Minyomerus} sec. Jansen \& Franz, 2018, we describe the following four species as new to science: \textit{Minyomerus ampullaceus} sec. Jansen \& Franz, 2018 (henceforth: [JF2018]), \textbf{new species,} \textit{Minyomerus franko} [JF2018], \textbf{new species,} \textit{Minyomerus sculptilis} [JF2018], \textbf{new species,} and \textit{Minyomerus tylotos} [JF2018], \textbf{new species.}
	The four new species are added to, and integrated with, the preceding revision, and an updated key and phylogeny of \textit{Minyomerus} [JF2018] are presented. 
	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (Length = 99 steps, Consistency Index = 60, Retention Index = 80). 
	The analysis reaffirms the monophyly of \textit{Minyomerus} [JF2018] with eight unreversed synapomorphies.
	The species-group placements, possible biogeographic origins, and natural history of the new species are discussed in detail.
\end{abstract}

@@

\section*{Introduction}\label{sec:intro}
	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. 
	Accordingly:

@@

		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively \citep{nixon2002}.
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA \citep{goloboff1999}.
		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
		Finally, Bremer support values \citep{bremer1994} and relative fit difference \citep{goloboff2001} were calculated in NONA using the commands: \texttt{hold 1001}, \texttt{sub 20}, \texttt{bs} for Bremer support values, and \texttt{bs*} for relative fit difference, respectively \citep{goloboff2008}.

@@

	\subsection*{Taxonomic annotations and RCC--5}\label{ssec:taxanno} 
		In accordance with \citet{jansen2015}, we use the symbol "=" to indicate nomenclatural synonymy (objective/subjective); and the RCC--5 symbols \{$==$, $>$, $<$, $><$, !\} indicate taxonomic concept articulations.
		The annotations (INT) and (OST) indicate intensional and ostensive readings of articulations, and AND is used to connect multiple simultaneously recognized provenance relationships.
		Two \emph{intensional} alignments are produced as part of this revision, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.

@@

	\subsection*{Species distribution modeling}\label{ssec:dismo} 
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
			Species of \textit{Minyomerus} [JF2018] are only known to be phytophagous, not parasitic, phoretic, or necrophagous. Hence we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.

@@

				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{CMNC}}: 1 \female, 1 \male);

@@

			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]).

@@

				Scape extending Brassicaceae  to posterior 1/4 of eye.

@@

				``Milner, Idaho; \#5a, 7-9-31; \textit{S.}[\textit{alsola}] \textit{pestifer}; David E. Fox'' (\texttt{\textbf{USNM}}: 1 \female);

@@

\section*{Checklist of Species}\label{sec:checklist}
	RCC--5 articulations are provided in \textbf{bold font.} See \citet{jansen2015} for alignments of \textit{Minyomerus} concepts published from 1831 to 2015.

@@

			\>\textbf{ \textit{gravivultus}} Jansen \& Franz, 2015: 92 sec. Jansen \& Franz (2015)\\

@@

\section*{Phylogenetic Results}\label{sec:results}
	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab.~\ref{tab:table1}).
	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}; see Figs.~\ref{fig:tree1}-\ref{fig:tree2}.
	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree1}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node. In a complementary graph, we show the herein used clade concept labels (Fig.~\ref{fig:tree2}).

	The characters, states, and preferred optimizations are described in this section.
	Characters relating to placement of the herein described taxa are discussed in detail in the \textbf{\nameref{sec:disc}} section, along with changes in species group composition and tree topology from \citet{jansen2015}.
	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
	Characters are numbered in accordance with descriptive sequence used in the species accounts.
	A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
	Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.

@@

	 	\item Prementum, anterior margin forming a distinct face that continues to lateral margins: (0) absent; (1) present. Synapomorphy for the \textit{M. aeriballux}--\textit{M. languidus} clade [JF2015], with a single reversal in the  \textit{M. caseyi}--\textit{M. trisetosus} clade [JF2015] (ci = 50; ri = 75).

@@

		\item Legs, relative length of mesotarsi to mesotibiae: (0) tarsi much shorter than tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi slightly shorter than tibiae. Coded as additive due to alignment of character states with preferred phylogeny. Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny. State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].

@@

	The first, classification-based alignment (Fig.~\ref{fig:align1}) is simple and straightforward to interpret (see also \textbf{Supplemental Information SI2}). 
	We obtain high-level congruence among the concepts \textit{Minyomerus} [JF2018] and \textit{Minyomerus} [JF2015], where 17 species-level concepts are retained from \citet{jansen2015} and four species-level concepts are added in the current revision.
	The coverage constraint is relaxed for \textit{Minyomerus} [JF2015], thus allowing the four new species-level concepts to be subsumed under this parent.
	This is based on our assertion that they fall under the generic character circumscription of \citet{jansen2015}.

@@

\section*{Acknowledgments}
	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens used in this revision.
	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.
	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).

@@

>>>>

\begin{abstract}
	This contribution adopts the taxonomic concept approach, including the use of \textit{taxonomic concept labels} (name sec. [\textit{according to}] source) and Region Connection Calculus (RCC--5) articulations and alignments. 
	Prior to this study, the broad-nosed weevil genus \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) contained 17 species distributed throughout the desert and plains regions of North America.
	In this review of \textit{Minyomerus} sec. Jansen \& Franz, 2018, we describe the following four species as new to science: \textit{Minyomerus ampullaceus} sec. Jansen \& Franz, 2018 (henceforth: [JF2018]), \textbf{new species,} \textit{Minyomerus franko} [JF2018], \textbf{new species,} \textit{Minyomerus sculptilis} [JF2018], \textbf{new species,} and \textit{Minyomerus tylotos} [JF2018], \textbf{new species.}
	The four new species are added to, and integrated with, the preceding revision, and an updated key and phylogeny of \textit{Minyomerus} [JF2018] are presented. 
	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (Length = 99 steps, Consistency Index = 60, Retention Index = 80). 
	The analysis reaffirms the monophyly of \textit{Minyomerus} [JF2018] with eight unreversed synapomorphies.
	The species-group placements, possible biogeographic origins, and natural history of the new species are discussed in detail.
\end{abstract}

@@

\section*{Introduction}\label{sec:intro}
	This phylogenetic study follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. 
	Accordingly:

@@

		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively \citep{nixon2002}.
		Characters are numbered in accordance with descriptive sequence used in the species accounts.
		A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
		Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.
		All multi-state characters but one were coded as additive, as explained beneath the description for each character (see \textbf{\nameref{sec:results}}), based on their alignment with the preferred phylogeny.
		Each alternative coding scheme was tested both alone and in unison with the other multi-state characters to assess their impact on the topology of the preferred phylogeny.

		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA \citep{goloboff1999}.
		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
		Finally, Bremer support values \citep{bremer1994} and relative fit difference \citep{goloboff2001} were calculated in NONA using the commands: \texttt{hold 1001}, \texttt{sub 20}, \texttt{bs} for Bremer support values, and \texttt{bs*} for relative fit difference, respectively \citep{goloboff2008}.

@@

	\subsection*{Taxonomic annotations and RCC--5}\label{ssec:taxanno} 
		In accordance with \citet{jansen2015}, we use the symbol "=" to indicate nomenclatural synonymy (objective/subjective); and the RCC--5 symbols \{$==$, $>$, $<$, $><$, !\} indicate taxonomic concept articulations.
		The annotations (INT) and (OST) indicate intensional and ostensive readings of articulations, and AND is used to connect multiple simultaneously recognized provenance relationships.
		Two \emph{intensional} alignments are produced as part of this review, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.

@@

	\subsection*{Species distribution modeling}\label{ssec:dismo} 
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of \textit{Minyomerus} [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner. We had initially believed that this indicated a specimen found in a roadrunner nest; however, according to our reviewers, the USNM frequently assisted with the identification of insect specimens retrieved from the stomach contents of birds, and thus the specimen was most likely retrieved from the gut contents of a roadrunner. This seems quite likely given the poor external condition of the specimen.

@@

				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{USNM}}: 1 \female; \texttt{\textbf{CMNC}}: 1 \male);

@@

			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]). The indication of ``Sphaeralcea hastula A. Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata}.

@@

				Scape extending to posterior 1/4 of eye.

@@

				``Milner, Idaho; \#5a, 7-9-31; \textit{S.}[\textit{alsola}] \textit{pestifer}; David E. Fox'' (\texttt{\textbf{CMNC}}: 1 \female);

@@

\section*{Checklist of Species}\label{sec:checklist}
	RCC--5 articulations are provided in \textbf{bold font.} See \citet{jansen2015} for alignments of \textit{Minyomerus} concepts published from 1831 to 2015.

@@

			\> \textbf{\textit{gravivultus}} Jansen \& Franz, 2015: 92 sec. Jansen \& Franz (2015)\\

@@

\newpage
\section*{Phylogenetic Results}\label{sec:results}
	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab.~\ref{tab:table1}).
	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}; see Figs.~\ref{fig:tree1}-\ref{fig:tree2}.
	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree1}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node. In a complementary graph, we show the herein used clade concept labels (Fig.~\ref{fig:tree2}).

	The characters, states, and preferred optimizations are described in this section.
	Characters relating to placement of the herein described taxa are discussed in detail in the \textbf{\nameref{sec:disc}} section, along with changes in species group composition and tree topology from \citet{jansen2015}.
	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.

@@

	 	\item Prementum, anterior margin medially with a distinct facet, rather than a single edge edge, that continues to lateral margins: (0) absent; (1) present. Synapomorphy for the \textit{M. aeriballux}--\textit{M. languidus} clade [JF2015], with a single reversal in the  \textit{M. caseyi}--\textit{M. trisetosus} clade [JF2015] (ci = 50; ri = 75).

@@

		\item Legs, relative length of mesotarsi to mesotibiae: (0) tarsi less than 3/4\x length of tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi shorter than tibiae, but longer than 3/4\x length of tibiae. Coded as additive due to alignment of character states with preferred phylogeny. Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny. State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].

@@

	The first, classification-based alignment (Fig.~\ref{fig:align1}) is simple and straightforward to interpret (see also \textbf{Supplemental Information SI2}). 
	We obtain high-level congruence among the concepts \textit{Minyomerus} [JF2018] and \textit{Minyomerus} [JF2015], where 17 species-level concepts are retained from \citet{jansen2015} and four species-level concepts are added in the current review.
	The coverage constraint is relaxed for \textit{Minyomerus} [JF2015], thus allowing the four new species-level concepts to be subsumed under this parent.
	This is based on our assertion that they fall under the generic character circumscription of \citet{jansen2015}.

@@

\section*{Acknowledgments}
	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens used in this study.
	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.

@@

\section*{Funding statement}
	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
	There was no additional external funding received for this study.
